### 2017-07-26 sigplanconf-template.tex
Draft of introduction

%-----------------------------------------------------------------------------
%
%               Template for sigplanconf LaTeX Class
%
% Name:         sigplanconf-template.tex
%
% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
%               file for SIGPLAN conference proceedings.
%
% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
%               sigplanconf-guide.pdf
%
% Author:       Paul C. Anagnostopoulos
%               Windfall Software
%               978 371-2316
%               paul@windfall.com
%
% Created:      15 February 2005
%
%-----------------------------------------------------------------------------

\documentclass[preprint]{sigplanconf}
% The following \documentclass options may be useful:
% preprint       Remove this option only once the paper is in final form.
%  9pt           Set paper in  9-point type (instead of default 10-point)
% 11pt           Set paper in 11-point type (instead of default 10-point).
% numbers        Produce numeric citations with natbib (instead of default author/year).
% authorversion  Prepare an author version, with appropriate copyright-space text.
\usepackage{amsmath}

\newcommand{\cL}{{\cal L}}

\begin{document}

\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

\conferenceinfo{CONF'yy}{Month d--d, 20yy, City, ST, Country}
\copyrightyear{20yy}
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}\reprintprice{\$15.00}
\copyrightdoi{nnnnnnn.nnnnnnn}

% For compatibility with auto-generated ACM eRights management
% instructions, the following alternate commands are also supported.
%\CopyrightYear{2016}
%\conferenceinfo{CONF'yy,}{Month d--d, 20yy, City, ST, Country}
%\isbn{978-1-nnnn-nnnn-n/yy/mm}\acmPrice{\$15.00}
%\doi{http://dx.doi.org/10.1145/nnnnnnn.nnnnnnn}

% Uncomment the publication rights used.
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}  % default
%\setcopyright{rightsretained}

\titlebanner{banner above paper title}        % These are ignored unless
\preprintfooter{short description of paper}   % 'preprint' option specified.

\title{Title Text\titlenote{with optional title note}}
\subtitle{Subtitle Text, if any\titlenote{with optional subtitle note}}

\authorinfo{Name1\thanks{with optional author note}}
           {Affiliation1}
           {Email1}
\authorinfo{Name2 \and Name3\thanks{with optional author note}}
           {Affiliation2/3}
           {Email2/3}

\maketitle

\begin{abstract}
This is the text of the abstract.
\end{abstract}

% 2012 ACM Computing Classification System (CSS) concepts
% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011008</concept_id>
<concept_desc>Software and its engineering~General programming languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003752.10010124.10010138.10010143</concept_id>
<concept_desc>Theory of computation~Program analysis</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~General programming languages}
\ccsdesc[300]{Theory of computation~Program analysis}
% end generated code

% Legacy 1998 ACM Computing Classification System categories are also
% supported, but not recommended.
%\category{CR-number}{subcategory}{third-level}[fourth-level]
%\category{D.3.0}{Programming Languages}{General}
%\category{F.3.2}{Logics and Meanings of Programs}{Semantics of Programming Languages}[Program analysis]

\keywords
keyword1, keyword2

\section{Introduction}
	Understanding how a software system works is important in designing, implementing, and using it. Software architecture can be defined as the “fundamental organization of a system embodied in its components, their relations to each other, and the environment.” Any system, including a living organism can be understood from different perspectives and views; a human being can be analyzed in terms of his or her comprising systems as in the cardiovascular system or nervous system, or as a part of a larger structure, like a friendship, society, or species.

	A single software system can similarly be interpreted as a composite whole or a part of a larger system.  The software architecture of a system, or its “fundamental organization … embodied in its components, their relationship to each other, and to the environment, and the principles guiding its design and evolution,” is comprised of three basic levels. Software is comprised of three general architecture views: Software can be understood as sets of implementation units and sets of runtime components that have behavior and interact with one another, as well as in terms of its interactions with non-software elements, like hardware. These views are concisely called the Module, Component-and-Connector, and Allocation views respectively. Understanding a software system in terms of code-implementation (how it works), runtime entities (how it interacts with itself), and non-software interactions (how it interacts with non-software parts of a system) is crucial for its initial design and implementation, later adaptation, and use.

	While architecture is essential to developing, adapting, and understanding a software system, current software architecture practices provide few and weaker-than-desirable guarantees that architecture views reflect what happens when a system is in use. When a developer initially designs her software system, she might draw up a graph representing various components and their relationships. Whether the components are set of programmatic code pieces, runtime elements, or system parts depends on what stage of development and from what architecture view she is approaching the design. While the logical relationships between these theoretical elements are sound, their realization may present some issues.

	For example, when designing a <SYSTEM>, one might draw up a graph representing the intended Component-and-Connector (CnC) view, including the components, or the <LIST OF COMPONENTS> and the connectors, or the <LIST OF CONNECTORS>. However a conflict between the <CONNECTOR TYPE> connector and the <COMPONENT> forces the developer to change the architecture during implementation. Depending on the effects of this change and others like it, the realization may not uphold the guarantees of the intended architecture. In the aforementioned example, the planned <CONNECTOR TYPE> connector ensured that the <COMPONENT> could only communicate with the <OTHER COMPONENT> in a specific way. While implementation adjustments were required for completion, the assumptions from the original architecture about how COMPONENT1 is able to communicate with other runtime components may no longer hold. Here, communication integrity is no longer guaranteed.

	Software system designs must adapt as the problem or understanding of it changes. This type of adaptability is essential for building software, but it also makes verifying intended software guarantees, such as communication integrity, difficult. Understanding how a software system works in practice, as opposed to theoretically, is necessary when developing, adapting, and using it.

\appendix
\section{Appendix Title}

This is the text of the appendix, if you need one.

\acks

Acknowledgments, if needed.

% The 'abbrvnat' bibliography style is recommended.

\bibliographystyle{abbrvnat}

% The bibliography should be embedded for final submission.

\begin{thebibliography}{}
\softraggedright

\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
P. Q. Smith, and X. Y. Jones. ...reference text...

\end{thebibliography}

\end{document}

### 2017-07-27 sigplanconf-template.tex
Early Design Section added

@@
 \section{Introduction}
+
 	Understanding how a software system works is important in designing, implementing, and using it.
@@
 
+\section{Early Design}
+
+	As a solution to the issue of carrying intended architecture guarantees through to the final implementation, we present Trinity, an extension to the Wyvern programming language that aims to make software architecture views a presecriptive, rather than simply descriptive, aspect of a software system in Wyvern.
+Trinity incorporates architecture in a unique way, making it a “live” component: software systems can have hard-coded architectures for all three architecture views.
+Instead of providing a descriptive architecture that attempts to explain how a system functions, Trinity supports architecture as a language construct in Wyvern.
+In the case of the CnC architectural view, what would conventionally be only logical organizations and distinctions between components and connectors, can now be actually implemented components and connectors.
+Since Trinity supports prescriptive software architecture views it allows developers to catch architecture-related errors at compile time, rather than runtime.
+This novel ability enables safer inspection for vulnerabilities originating in architecture flaws.
+
 \appendix

### 2017-07-27 sigplanconf-template.tex
more of Early Design + title

@@
 
-\title{Title Text\titlenote{with optional title note}}
+\title{Trinity: A Language for Multi-View Architecture Description and Control\titlenote{with optional title note}}
 \subtitle{Subtitle Text, if any\titlenote{with optional subtitle note}}
@@
 
+	Trinity is designed to safeguard communication integrity, which is a top priority in regards to desired guarantees to preserve in end-product implementations.
+To enforce communication integrity is to ensure that “each component in [an] implementation may [communicate] directly with … components to which it is connected in the architecture.” In our early implementation of Trinity, we have provided support for a “hard-coded” Component-and-Connector view of a Wyvern software system.
+Our design translates concepts from software architecture into implementation capabilities.
+
+	Entities in the Cnc architecture view are keywords/types/objects in Trinity.
+An entire software architecture, comprised of components and connectors, is contained within an architecture object/type/keyword.
+Trinity components are runtime components such as servers, clients, and databases.
+Ports are fields of a component that act as access points to interact with other components; these include interfaces that provide details about the interface another component must fulfill to communicate with said component through said port.
+Connectors, such as JDBC connectors, connect multiple ports of components.
+Attachments allow the programmer to “actually” connect components using ports of components and provided connectors.
+An entryPoint is an access point for a program using the specified architecture.
+It might be a function of a particular component in the architecture.
+For example, an architecture describing a three-tier web application might have an entryPoint specified by the “start()” function of a client component.
+Bindings allow the programmer to alias functions of components, to reduce code verbosity.
+
 \appendix

### 2017-07-27 sigplanconf-template.tex
commented out some excess template

@@
 
-\title{Trinity: A Language for Multi-View Architecture Description and Control\titlenote{with optional title note}}
+\title{Trinity: A Language for Multi-View Architecture Description and Control}%\titlenote{with optional title note}}
 \subtitle{Subtitle Text, if any\titlenote{with optional subtitle note}}
 
-\authorinfo{Name1\thanks{with optional author note}}
+\authorinfo{Name1}%\thanks{with optional author note}}
            {Affiliation1}
            {Email1}
-\authorinfo{Name2 \and Name3\thanks{with optional author note}}
+\authorinfo{Name2 \and Name3}%\thanks{with optional author note}}
            {Affiliation2/3}
@@
 
-\ccsdesc[500]{Software and its engineering~General programming languages}
-\ccsdesc[300]{Theory of computation~Program analysis}
+%%% *** COMMENTED OUT ***
+%\ccsdesc[500]{Software and its engineering~General programming languages}
+%\ccsdesc[300]{Theory of computation~Program analysis}
 % end generated code
@@
 
-\keywords
-keyword1, keyword2
+%%% COMMENTED OUT
+%\keywords
+%keyword1, keyword2
 

### 2017-07-28 sigplanconf-template.tex
draft of Early Design section

@@
 
+	We have implemented a simple three-tier web application example of Trinity’s encoded architecture, including server and client components.
+The server is connected to a database, which is external component or a component only accessible by [INSERT HERE].
+The client can only interact with the database through its own getInfo port, which is a client method, that corresponds to the server’s sendInfo method port.
+The server’s JSON connector gives it access to the database, which provides the client’s indirect channel of communication with the database.
+
+	While the programmer provides client and server interface code, Trinity generates code for the server’s connector, whose type is specified by the programmer.
+In our example, JSON connector code is generated.
+Referring to the architecture’s attachments the Trinity parser type checks the connect expression and the types of the requires and provides ports of the client and server respectively are matched.
+Then the metadata associated with the JSON connector specifies the code that must be emitted for coordinating between the requires and provides ports.
+The code for the client’s getInfo port, the server’s sendInfo port, and serializing and deserializing to and from JSON is generated.
+By allotting communication-integrity sensitive code to Trinity automatic code generation, we ensure that communication integrity between the client and database is enforced.
+
 \appendix

### 2017-07-29 sigplanconf-template.tex
Edited Early Design section
Wiped

--- 2017-07-27 sigplanconf-template.tex
@@
 
-	Understanding how a software system works is important in designing, implementing, and using it.
-Software architecture can be defined as the “fundamental organization of a system embodied in its components, their relations to each other, and the environment.” Any system, including a living organism can be understood from different perspectives and views; a human being can be analyzed in terms of his or her comprising systems as in the cardiovascular system or nervous system, or as a part of a larger structure, like a friendship, society, or species.
-
-	A single software system can similarly be interpreted as a composite whole or a part of a larger system.
-The software architecture of a system, or its “fundamental organization … embodied in its components, their relationship to each other, and to the environment, and the principles guiding its design and evolution,” is comprised of three basic levels.
-Software is comprised of three general architecture views: Software can be understood as sets of implementation units and sets of runtime components that have behavior and interact with one another, as well as in terms of its interactions with non-software elements, like hardware.
-These views are concisely called the Module, Component-and-Connector, and Allocation views respectively.
-Understanding a software system in terms of code-implementation (how it works), runtime entities (how it interacts with itself), and non-software interactions (how it interacts with non-software parts of a system) is crucial for its initial design and implementation, later adaptation, and use.
-
-	While architecture is essential to developing, adapting, and understanding a software system, current software architecture practices provide few and weaker-than-desirable guarantees that architecture views reflect what happens when a system is in use.
-When a developer initially designs her software system, she might draw up a graph representing various components and their relationships.
-Whether the components are set of programmatic code pieces, runtime elements, or system parts depends on what stage of development and from what architecture view she is approaching the design.
-While the logical relationships between these theoretical elements are sound, their realization may present some issues.
-
-	For example, when designing a <SYSTEM>, one might draw up a graph representing the intended Component-and-Connector (CnC) view, including the components, or the <LIST OF COMPONENTS> and the connectors, or the <LIST OF CONNECTORS>.
-However a conflict between the <CONNECTOR TYPE> connector and the <COMPONENT> forces the developer to change the architecture during implementation.
-Depending on the effects of this change and others like it, the realization may not uphold the guarantees of the intended architecture.
-In the aforementioned example, the planned <CONNECTOR TYPE> connector ensured that the <COMPONENT> could only communicate with the <OTHER COMPONENT> in a specific way.
-While implementation adjustments were required for completion, the assumptions from the original architecture about how COMPONENT1 is able to communicate with other runtime components may no longer hold.
-Here, communication integrity is no longer guaranteed.
-
-	Software system designs must adapt as the problem or understanding of it changes.
-This type of adaptability is essential for building software, but it also makes verifying intended software guarantees, such as communication integrity, difficult.
-Understanding how a software system works in practice, as opposed to theoretically, is necessary when developing, adapting, and using it.
-
 \section{Early Design}
-
-	As a solution to the issue of carrying intended architecture guarantees through to the final implementation, we present Trinity, an extension to the Wyvern programming language that aims to make software architecture views a presecriptive, rather than simply descriptive, aspect of a software system in Wyvern.
-Trinity incorporates architecture in a unique way, making it a “live” component: software systems can have hard-coded architectures for all three architecture views.
-Instead of providing a descriptive architecture that attempts to explain how a system functions, Trinity supports architecture as a language construct in Wyvern.
-In the case of the CnC architectural view, what would conventionally be only logical organizations and distinctions between components and connectors, can now be actually implemented components and connectors.
-Since Trinity supports prescriptive software architecture views it allows developers to catch architecture-related errors at compile time, rather than runtime.
-This novel ability enables safer inspection for vulnerabilities originating in architecture flaws.
-
-	Trinity is designed to safeguard communication integrity, which is a top priority in regards to desired guarantees to preserve in end-product implementations.
-To enforce communication integrity is to ensure that “each component in [an] implementation may [communicate] directly with … components to which it is connected in the architecture.” In our early implementation of Trinity, we have provided support for a “hard-coded” Component-and-Connector view of a Wyvern software system.
-Our design translates concepts from software architecture into implementation capabilities.
-
-	Entities in the Cnc architecture view are keywords/types/objects in Trinity.
-An entire software architecture, comprised of components and connectors, is contained within an architecture object/type/keyword.
-Trinity components are runtime components such as servers, clients, and databases.
-Ports are fields of a component that act as access points to interact with other components; these include interfaces that provide details about the interface another component must fulfill to communicate with said component through said port.
-Connectors, such as JDBC connectors, connect multiple ports of components.
-Attachments allow the programmer to “actually” connect components using ports of components and provided connectors.
-An entryPoint is an access point for a program using the specified architecture.
-It might be a function of a particular component in the architecture.
-For example, an architecture describing a three-tier web application might have an entryPoint specified by the “start()” function of a client component.
-Bindings allow the programmer to alias functions of components, to reduce code verbosity.
 

### 2017-07-29 sigplanconf-template.tex
Design: Added example arch explanation

@@
 
-\section{Early Design}
+\section{Design}
+
+	Trinity is designed to unify software architecture design and implementation for not just a single architecture view, but in all three (module, component-and-connector, and deployment).
+
+	To demonstrate how Trinity makes software architecture “live” in Wyvern systems, we have implemented a simple 3-tier web application whose abridged code is shown in Figure 1.
+In overview, a database is accessed by a server that handles requests from a client.
+The example architecture contains two components, the client and server.
+As in more theoretical software architecture, components are runtime entities that may have ports  that act as access points to interact with other components.
+Our example server and client each have complementary ports, sendInfo and getInfo respectively, that enable interact; here, the server can send information to the client using a JSON connector responsible for serialization and deserialization.
+Note that Trinity connectors enable the joining two compatible component ports, analogous to ports in software architecture.
+The architecture’s attachments section actually/physically connects the client and the server using their matching ports and the JSON connector.
+
+	The client and server have their own component-specific architectures given before the general architecture code.
+Both components have corresponding ports that depend on a client-server interface, denoted by the “requires/provides CSIface” types of each port.
+This interface is required of a server by the client, as stated by the “requires CSIFace” type, and the server fulfills it, as shown by the “provides CSIface” server port type.
+The database is an external component of the server, which differs from a component in that the programmer does not provide its source code.
+“port dbIface: requires DBModule” The database and server are connected by a JDBC connector.
+This is used within a sub-architecture of the server that connects a specified request handler and the database.
+Finally, the bindings section of the server’s sub-architecture specifies that the client-facing port, sendInfo, of the server component is indeed the same sendInfo port of the request handler.
 

### 2017-07-29 sigplanconf-template.tex
added beta code snippet

@@
 \usepackage{amsmath}
+\usepackage{listings}
+\usepackage{xcolor}
 
+\colorlet{light-gray}{gray!20}
 \newcommand{\cL}{{\cal L}}
@@
 
+\begin{figure}
+
+	\begin{lstlisting}[frame=single, backgroundcolor=\color{light-gray}, basicstyle=\footnotesize\ttfamily, numbers=left, numberstyle=\tiny\color{black},caption= {Simple 3-tier web application architecture}]
+component Client
+	port getInfo: requires CSIface
+
+component Server
+	port sendInfo: provides CSIface
+
+external component DB
+	port dbIface: target DBModule
+
+connector JDBCCtr
+	val connectionString: String
+
+architecture 
+	components
+		RequestHandler ch
+		DB db
+
+connectors 
+	JDBCCtr jdbcCtr
+
+attachments
+	connect rh.dbIface and db.dbIface 
+		with jdbcCtr
+
+bindings 
+	sendInfo is rh.sendInfo
+
+architecture 	
+	components
+		Client client
+		Server server
+
+	connectors
+		JSONCtr jsonCtr
+
+	attachments 
+		Connect client.getInfo 
+		and server.sendInfo with jsonCtr
+
+	entryPoints
+		Client: start
+	\end{lstlisting}
+
+\end{figure}
+
 	Trinity is designed to unify software architecture design and implementation for not just a single architecture view, but in all three (module, component-and-connector, and deployment).

### 2017-08-01 paper.tex
Selva add

--- 2017-07-29 sigplanconf-template.tex
@@
 \documentclass[preprint]{sigplanconf}
+
 % The following \documentclass options may be useful:
+
 % preprint       Remove this option only once the paper is in final form.
@@
 % authorversion  Prepare an author version, with appropriate copyright-space text.
+
 \usepackage{amsmath}
@@
 \newcommand{\cL}{{\cal L}}
+\newcommand{\langname}{Trinity}
 
@@
 
-\title{Trinity: A Language for Multi-View Architecture Description and Control}%\titlenote{with optional title note}}
-\subtitle{Subtitle Text, if any\titlenote{with optional subtitle note}}
+%\title{Title Text\titlenote{with optional title note}}
+\title{\langname: A Language for Multi-View Architecture Description and Control}
+%\subtitle{Subtitle Text, if any\titlenote{with optional subtitle note}}
 
-\authorinfo{Name1}%\thanks{with optional author note}}
-           {Affiliation1}
-           {Email1}
-\authorinfo{Name2 \and Name3}%\thanks{with optional author note}}
-           {Affiliation2/3}
-           {Email2/3}
+%\authorinfo{Name1\thanks{with optional author note}}
+%           {Affiliation1}
+%           {Email1}
+%\authorinfo{Name2 \and Name3\thanks{with optional author note}}
+%           {Affiliation2/3}
+%           {Email2/3}
+\authorinfo{Jonathan Aldrich}
+           {Carnegie Mellon University}
+           {jonathan.aldrich@cs.cmu.edu}
+\authorinfo{Madaline Kirwin}
+           {Grinnell College}
+           {kirwinma@grinnell.edu}
+\authorinfo{Selva Samuel}
+           {Carnegie Mellon University}
+           {ssamuel@cs.cmu.edu}
 
@@
 
-%%% *** COMMENTED OUT ***
-%\ccsdesc[500]{Software and its engineering~General programming languages}
-%\ccsdesc[300]{Theory of computation~Program analysis}
+\ccsdesc[500]{Software and its engineering~General programming languages}
+\ccsdesc[300]{Theory of computation~Program analysis}
 % end generated code
@@
 
-%%% COMMENTED OUT
-%\keywords
-%keyword1, keyword2
+\keywords
+keyword1, keyword2
 
-\section{Introduction}
+%\section{Introduction}
 
-\section{Early Design}
+%The text of the paper begins here.
 
-\appendix
-\section{Appendix Title}
+\section{Multiple Views of Software Architecture}
+
+\begin{itemize}
+\renewcommand\labelitemi{--}
+\item Give the SEI definition of software architecture
+\item State the usefulness of software architecture in analysis and design activities
+\item Introduce ADLs.
+\item Introduce views. State their usefulness in dealing with complexity by separating concerns
+\item State the lack of support for multiple views in ADLs.
+\item State that industry practitioners desire support for multiple views. Cite study by Malavolta et. al.
+\end{itemize}
+The software architecture of a system is the set of structures needed to reason about the system, which comprise software elements, relations among them, and properties of both [].
+
+%Most software architectures are implicit.
+
+%UML
+\cite{Malavolta2013}
+
+\section{Architectural Control}
+\begin{itemize}
+\renewcommand\labelitemi{--}
+\item What is architectural control? --$>$ Architectural constraints must be enforced in the implementation
+\item Introduce communication integrity
+\item Describe ArchJava's support for enforcing communication integrity in a single JVM and its failure to do so across multiple JVMs
+\end{itemize}
+\section{\langname}
+
+%\appendix
+%\section{Appendix Title}
 
@@
 \bibliographystyle{abbrvnat}
+\bibliography{references.bib}
 
@@
 
-\begin{thebibliography}{}
-\softraggedright
+%\begin{thebibliography}{}
+%\softraggedright
 
-\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
-P. Q. Smith, and X. Y. Jones. ...reference text...
+%\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
+%P. Q. Smith, and X. Y. Jones. ...reference text...
 
-\end{thebibliography}
+%\end{thebibliography}
 

### 2017-08-12 paper.tex
Test pushing
Use numbers in citations instead of author-year
Everything I have written till now

@@
 
-\documentclass[preprint]{sigplanconf}
+\documentclass[numbers,preprint]{sigplanconf}
 
@@
 \usepackage{amsmath}
+\usepackage{caption}
+\usepackage{color}
+\usepackage{listings}
+\usepackage{url}
 
@@
 \newcommand{\langname}{Trinity}
+\newcommand{\moduleview}{module}
+\newcommand{\Moduleview}{Module}
+
+\definecolor{gray}{RGB}{128, 128, 128}
+
+\lstdefinestyle{modulestyle}{
+	basicstyle=\scriptsize
+}
+
+\lstdefinestyle{cncstyle}{
+	aboveskip=0pt,
+	belowskip=-10pt,
+	basicstyle=\footnotesize\ttfamily,
+	captionpos=b,
+	columns=flexible,
+	float=t,
+	frame=single,
+	morekeywords={component},
+	keywordstyle=\color{blue},
+	numbers=left,
+	numberstyle=\color{gray}\scriptsize\fontfamily{cmr}\selectfont,
+	numbersep=8pt,
+	tabsize=2,
+	xleftmargin=19pt,
+	framexleftmargin=15pt,
+	framexrightmargin=-4pt
+}
+
+\lstdefinelanguage{cnclang}{
+	morekeywords={component, port},
+}
+
+\lstdefinestyle{allocationstyle}{
+}
+
+\DeclareCaptionFormat{listing}{\textbf{#1.} #3}
+\captionsetup[lstlisting]{format=listing}
 
@@
 
-\titlebanner{banner above paper title}        % These are ignored unless
+%\titlebanner{banner above paper title}        % These are ignored unless
 \preprintfooter{short description of paper}   % 'preprint' option specified.
@@
 %           {Email2/3}
-\authorinfo{Jonathan Aldrich}
-           {Carnegie Mellon University}
-           {jonathan.aldrich@cs.cmu.edu}
-\authorinfo{Madaline Kirwin}
-           {Grinnell College}
-           {kirwinma@grinnell.edu}
-\authorinfo{Selva Samuel}
-           {Carnegie Mellon University}
-           {ssamuel@cs.cmu.edu}
+%\authorinfo{Selva Samuel}
+%           {Carnegie Mellon University}
+%           {ssamuel@cs.cmu.edu}
+%\authorinfo{Madaline Kirwin}
+%           {Grinnell College}
+%           {kirwinma@grinnell.edu}
+%\authorinfo{Jonathan Aldrich}
+%           {Carnegie Mellon University}
+%           {jonathan.aldrich@cs.cmu.edu}
+\authorinfo{}{}{}
 
@@
 % Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10011007.10011006.10011008</concept_id>
-<concept_desc>Software and its engineering~General programming languages</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
-<concept_id>10003752.10010124.10010138.10010143</concept_id>
-<concept_desc>Theory of computation~Program analysis</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
+%\begin{CCSXML}
+%<ccs2012>
+%<concept>
+%<concept_id>10011007.10011006.10011008</concept_id>
+%<concept_desc>Software and its engineering~General programming languages</concept_desc>
+%<concept_significance>500</concept_significance>
+%</concept>
+%<concept>
+%<concept_id>10003752.10010124.10010138.10010143</concept_id>
+%<concept_desc>Theory of computation~Program analysis</concept_desc>
+%<concept_significance>300</concept_significance>
+%</concept>
+%</ccs2012>
+%\end{CCSXML}
 
-\ccsdesc[500]{Software and its engineering~General programming languages}
-\ccsdesc[300]{Theory of computation~Program analysis}
+%\ccsdesc[500]{Software and its engineering~General programming languages}
+%\ccsdesc[300]{Theory of computation~Program analysis}
 % end generated code
@@
 
-\keywords
-keyword1, keyword2
+%\keywords
+%keyword1, keyword2
 
@@
 
-\begin{itemize}
-\renewcommand\labelitemi{--}
-\item Give the SEI definition of software architecture
-\item State the usefulness of software architecture in analysis and design activities
-\item Introduce ADLs.
-\item Introduce views. State their usefulness in dealing with complexity by separating concerns
-\item State the lack of support for multiple views in ADLs.
-\item State that industry practitioners desire support for multiple views. Cite study by Malavolta et. al.
-\end{itemize}
-The software architecture of a system is the set of structures needed to reason about the system, which comprise software elements, relations among them, and properties of both [].
+%\begin{itemize}
+%\renewcommand\labelitemi{--}
+%\item Give the SEI definition of software architecture
+%\item State the usefulness of software architecture in analysis and design activities
+%\item Introduce ADLs.
+%\item Introduce views. State their usefulness in dealing with complexity by separating concerns
+%\item State the lack of support for multiple views in ADLs.
+%\item State that industry practitioners desire support for multiple views. Cite study by Malavolta et. al.
+%\end{itemize}
+The software architecture of a system is the set of structures needed to reason about the system, each consisting of elements of the system, relations among them, and properties of both \cite{SEISwArchDef}.
+Software architecture enables the system designers to analyze the system's ability to meet quality objectives like performance, reliability, etc.
+Thus, it facilitates the early detection of design errors and leads to improved software quality.
+It also provides a blueprint for system implementation and evolution.
 
+To facilitate the different uses of software architecture in system development activities, a number of architecture description languages (ADLs) have been developed \cite{ADLs}.
+ADLs are formal languages that can be used to represent the architecture of a software system in an unambiguous way.
+Thus, they provide a rigorous basis for the analysis of system designs.
+ADLs also enable the various stakeholders to understand the system better and thus aid in system implementation, maintenance and evolution.
+
+System designers often organize the architecture description of a software system as a set of views.
+An architectural view is a representation of those elements of the system that are needed to show how the architecture addresses a concern held by one or more stakeholders.
+For example, to devise an implementation plan, the system designers might create a (\moduleview) view that shows the module decomposition of the system and the dependencies among the modules (i.e., implementation units).
+Moreover, this view would not include the system's runtime entities or elements from the system's deployment environment.
+The separation of concerns achieved by splitting the architectural description into different views helps keep the architecture description cognitively tractable.
+
+The vast majority of existing ADLs, however, lack support for multiple views.
+This hampers the use of ADLs for the specification of software architecture in practical settings.
+A survey conducted by \citeauthor{Malavolta2013} \cite{Malavolta2013} found that better support for multiple views is one of the features most desired by industrial practitioners in ADLs.
+
+%This is a limitation. Low expressiveness.
+
+%Software architecture has to address multiple concerns. Using a single model to reason about every concern would make it complex. To deal with this complexity, views are used.
+
+%A view is a representation of one or more structural aspects of an architecture that illustrates how the architecture addresses one or more concerns held by one or more of its stakeholders.
 %Most software architectures are implicit.
@@
 %UML
-\cite{Malavolta2013}
 
 \section{Architectural Control}
-\begin{itemize}
-\renewcommand\labelitemi{--}
-\item What is architectural control? --$>$ Architectural constraints must be enforced in the implementation
-\item Introduce communication integrity
-\item Describe ArchJava's support for enforcing communication integrity in a single JVM and its failure to do so across multiple JVMs
-\end{itemize}
+%\begin{itemize}
+%\renewcommand\labelitemi{--}
+%\item What is architectural control? --$>$ Architectural constraints must be enforced in the implementation
+%\item Introduce communication integrity
+%\item Describe ArchJava's support for enforcing communication integrity in a single JVM and its failure to do so across multiple JVMs
+%\end{itemize}
+
+Software architects design systems to meet quality attribute requirements like performance, reliability, security, etc.
+To guarantee that the implemented system exhibits the desired quality attributes, it is necessary to ensure that the implementation adheres to the design principles and constraints prescribed by the architecture.
+Architectural control is the ability of software architects to enforce architectural constraints on the implementation so that the system meets its design goals.
+
+\citeauthor{LV1995} have identified \textit{communication integrity} as a key aspect of maintaining consistency between the architecture and implementation of a software system \cite{LV1995}.
+Communication integrity is the property that each component in the implementation may communicate directly only with the components to which it is connected in the architecture.
+
+In prior work, ArchJava used a custom type system to verify communication integrity statically \cite{Aldrich2002}.
+A limitation of ArchJava is its inability to ensure that an application communicates over the network using only the connections shown in the architecture.
+Since programs in ArchJava have unrestricted access to system libraries, a component can use the network library directly to communicate in ways not specified in the architecture.
+
 \section{\langname}
+
+We are developing \langname, an ADL that would allow software architects to ...
+
+\noindent
+\\
+\textbf{Multi-View Architecture Description in \langname.} \citeauthor{Clements2010} \cite{Clements2010} identify three basic types of views: ...
+
+Trinity provides support for these three views.
+
+Module view:
+
+Component-and-connector view:
+
+Deployment view:
+
+\begin{lstlisting}[style=cncstyle, caption=Caption, label=cncview, language=cnclang]
+component Test
+	port port1
+	port port2
+\end{lstlisting}
+
+\lstlistingname~\ref{cncview}
+
+\noindent
+\\
+\textbf{Architectural Control in \langname.}
 
@@
 
-This is the text of the appendix, if you need one.
+%This is the text of the appendix, if you need one.
 
-\acks
+%\acks
 
-Acknowledgments, if needed.
+%Acknowledgments, if needed.
 

### 2017-08-12 paper.tex
Section 3

@@
 \lstdefinestyle{modulestyle}{
-	basicstyle=\scriptsize
+	aboveskip=0pt,
+	belowskip=-10pt,
+	basicstyle=\footnotesize\ttfamily,
+	captionpos=b,
+	belowcaptionskip=0pt,
+	columns=flexible,
+	float=t,
+	frame=single,
+	keywordstyle=\color{blue},
+	numbers=left,
+	numberstyle=\color{gray}\scriptsize\fontfamily{cmr}\selectfont,
+	numbersep=8pt,
+	tabsize=2,
+	xleftmargin=19pt,
+	framexleftmargin=15pt,
+	framexrightmargin=-4pt
+}
+
+\lstdefinelanguage{modulelang}{
+	morekeywords={resource, type, def, module, val, var}
 }
@@
 	captionpos=b,
+	belowcaptionskip=0pt,
 	columns=flexible,
@@
 	frame=single,
-	morekeywords={component},
 	keywordstyle=\color{blue},
@@
 \lstdefinelanguage{cnclang}{
-	morekeywords={component, port},
+	morekeywords={component, port, connector, val, architecture, components, connectors, connections, connect, and, with, entryPoints}
 }
@@
 \lstdefinestyle{allocationstyle}{
+	aboveskip=0pt,
+	belowskip=-10pt,
+	basicstyle=\footnotesize\ttfamily,
+	captionpos=b,
+	belowcaptionskip=0pt,
+	columns=flexible,
+	float=t,
+	frame=single,
+	keywordstyle=\color{blue},
+	numbers=left,
+	numberstyle=\color{gray}\scriptsize\fontfamily{cmr}\selectfont,
+	numbersep=8pt,
+	tabsize=2,
+	xleftmargin=19pt,
+	framexleftmargin=15pt,
+	framexrightmargin=-4pt
+}
+
+\lstdefinelanguage{allocationlang}{
+	morekeywords={deployment, extends}
 }
@@
 \captionsetup[lstlisting]{format=listing}
+
+% FIXME: Comment the following when you need to add copyright information.
+\makeatletter
+\def\@copyrightspace{\relax}
+\makeatother
 
@@
 
-\begin{abstract}
-This is the text of the abstract.
-\end{abstract}
+%\begin{abstract}
+%This is the text of the abstract.
+%\end{abstract}
 
@@
 
-Module view:
+\noindent
+\\
+\textit{\textbf{Module view.}} Module view is used to document the principal implementation units of a system, together with the relations among these units.
+The primary elements in module view are implementation units that provide a coherent set of responsibilities.
+In \langname, implementation units take the form of capability-based modules.
 
-Component-and-connector view:
+%Every module has a collection of properties associated with it.
+These properties are intended to express the important information associated with the module, as well as constraints on the module.
+Sample properties are responsibilities, visibility information, and author or owner.
 
-Deployment view:
+Modules are related to one another using the depends on relation.
 
-\begin{lstlisting}[style=cncstyle, caption=Caption, label=cncview, language=cnclang]
-component Test
-	port port1
-	port port2
+What is a module view useful for?
+The module view can be used to determine how a system's source code is decomposed into units, what assumptions each unit can make about services provided by other units, and how these units are aggregated into larger ensembles.
+The module view can thus be used to create an implementation plan and also to determine how changes to one part of a system might affect other parts and thus reason about the system's modifiability, portability and reuse.
+
+\begin{lstlisting}[style=modulestyle, caption=Module view of a client/server system, label=moduleview, language=modulelang]
+resource type CSIface
+	def getVal(key: String): String
+
+module def Client(cPlumbing: CSIface): ClientIface
+	def startClient(): Unit
+		...
+
+module def Server(sPlumb: SPlumbing): ServerIface
+	module def sendInfo(): CSIface
+		def getVal(key: String): String
+			...
+
+	def startServer(): Unit
+		sPlumb.setFn(sendInfo().getVal)
+		...
+\end{lstlisting}
+
+\noindent
+\\
+\textit{\textbf{Component-and-connector view.}} Component-and-connector view expresses runtime behavior.
+It is described in terms of components and connectors.
+A component is one of the principal processing units of the executing system.
+Components might be services, processes, threads, filters, repositories, peers, or clients and servers, to name a few.
+A connector is the interaction mechanism among components.
+Connectors include pipes, queues, request/reply protocols, direct invocation, event-driven invocation, etc.
+Components and connectors can be decomposed into other components and connectors.
+The decomposition of a component may include connectors and vice versa.
+
+\begin{lstlisting}[style=cncstyle, caption=C\&C view of the client/server system, label=cncview, language=cnclang]
+component Client
+	port getInfo: requires CSIface
+
+component Server
+	port sendInfo: provides CSIface
+
+connector JSONCtr
+	val host: IPAddress
+	val prt: Int
+
+architecture ClientServer
+	components
+		Client client
+		Server server
+
+	connectors
+		JSONCtr jsonCtr
+
+	connections
+		connect client.getInfo and server.sendInfo
+			with jsonCtr
+
+	entryPoints
+		client: startClient
+		server: startServer
+\end{lstlisting}
+
+\noindent
+\\
+\textit{\textbf{Allocation view.}} Allocation view describes the mapping of software units to elements of an environment in which the software is developed or executes.
+The environment might be the hardware, the file systems supporting development or deployment, or the development organization(s).
+
+\begin{lstlisting}[style=allocationstyle, caption=Allocation view of the client/server system, label=allocationview, language=allocationlang]
+deployment CSDeployment extends ClientServer
+	jsonCtr.host = 127.0.0.1
+	jsonCtr.port = 9090
+\end{lstlisting}
+
+\begin{lstlisting}[style=modulestyle, caption=Plumbing code generated for the client, label=clientplumbing, language=modulelang]
+module def cPlumbing(tcpClient: TCPClient): CSIface
+	def getVal(key: String): String
+		tcpClient.connect(IPAddress("127.0.0.1"), 9090)
+		...
+
+val tcpClient = TCPClient()
+val plumbing = cPlumbing(tcpClient)
+val c = client(plumbing)
+c.start()
 \end{lstlisting}
@@
 \lstlistingname~\ref{cncview}
+\cite{Nistor2013} \cite{Melicher2017}
 

### 2017-08-12 paper.tex
Section 3

--- 2017-08-12 paper.tex
@@
 \lstdefinestyle{modulestyle}{
-	basicstyle=\scriptsize
+	aboveskip=0pt,
+	belowskip=-10pt,
+	basicstyle=\footnotesize\ttfamily,
+	captionpos=b,
+	columns=flexible,
+	float=t,
+	frame=single,
+	keywordstyle=\color{blue},
+	numbers=left,
+	numberstyle=\color{gray}\scriptsize\fontfamily{cmr}\selectfont,
+	numbersep=8pt,
+	tabsize=2,
+	xleftmargin=19pt,
+	framexleftmargin=15pt,
+	framexrightmargin=-4pt
+}
+
+\lstdefinelanguage{modulelang}{
+	morekeywords={resource, type, def, module, val, var}
 }
@@
 \lstdefinestyle{allocationstyle}{
+	aboveskip=0pt,
+	belowskip=-10pt,
+	basicstyle=\footnotesize\ttfamily,
+	captionpos=b,
+	columns=flexible,
+	float=t,
+	frame=single,
+	keywordstyle=\color{blue},
+	numbers=left,
+	numberstyle=\color{gray}\scriptsize\fontfamily{cmr}\selectfont,
+	numbersep=8pt,
+	tabsize=2,
+	xleftmargin=19pt,
+	framexleftmargin=15pt,
+	framexrightmargin=-4pt
+}
+
+\lstdefinelanguage{allocationlang}{
+	morekeywords={deployment, extends}
 }
@@
 
+% FIXME: Comment the following when you need to add copyright information.
+\makeatletter
+\def\@copyrightspace{\relax}
+\makeatother
+
 \begin{document}
+\begin{sloppypar}
 
@@
 %\end{itemize}
-The software architecture of a system is the set of structures needed to reason about the system, each consisting of elements of the system, relations among them, and properties of both \cite{SEISwArchDef}.
+The software architecture of a system is the set of structures needed to reason about the system, each consisting of elements of the system, relations among them, and properties of both \cite{Clements2010}.
 Software architecture enables the system designers to analyze the system's ability to meet quality objectives like performance, reliability, etc.
@@
 
-We are developing \langname, an ADL that would allow software architects to ...
+We are developing \langname, an ADL that would allow software architects to describe the software architecture of a system using multiple views and to guarantee communication integrity even for applications that involve communication across processes, possibly over a network.
 
@@
 \\
-\textbf{Multi-View Architecture Description in \langname.} \citeauthor{Clements2010} \cite{Clements2010} identify three basic types of views: ...
-
+\textbf{Multi-View Architecture Description in \langname.} \citeauthor{Clements2010} \cite{Clements2010} identify three basic types of views: a) module view, b) component-and-connector view, and c) allocation view.
 Trinity provides support for these three views.
 
-Module view:
+\noindent
+\textit{\textbf{Module view.}} The module view is used to document the principal implementation units of a system, together with the relations among these units.
 
-Component-and-connector view:
+We have designed \langname{} to describe the architecture of systems implemented in the Wyvern programming language.
+Since Wyvern provides first-class modules \cite{Melicher2017} which can be instantiated, passed as arguments and returned from a function, we use module definitions in Wyvern to implicitly describe the module view by specifying the Wyvern modules that would be used for implementing the system and the dependencies among them.
 
-Deployment view:
+For example, \lstlistingname{} \ref{moduleview} shows the module view of a client-server system.
+It consists of a \texttt{Client} module and a \texttt{Server} module.
+The \texttt{Client} module depends on a module instance of type \texttt{CSIface} and the \texttt{Server} module depends on a module instance of type \texttt{SPlumbing}.
+%The primary elements in module view are implementation units that provide a coherent set of responsibilities. In \langname, implementation units take the form of capability-based modules.
 
-\begin{lstlisting}[style=cncstyle, caption=Caption, label=cncview, language=cnclang]
-component Test
-	port port1
-	port port2
+%Every module has a collection of properties associated with it.
+These properties are intended to express the important information associated with the module, as well as constraints on the module.
+Sample properties are responsibilities, visibility information, and author or owner.
+
+%Modules are related to one another using the depends on relation.
+
+%What is a module view useful for?
+The module view can be used to determine how a system's source code is decomposed into units, what assumptions each unit can make about services provided by other units, and how these units are aggregated into larger ensembles.
+The module view can thus be used to create an implementation plan and also to determine how changes to one part of a system might affect other parts and thus reason about the system's modifiability, portability and reuse.
+
+\begin{lstlisting}[style=modulestyle, caption=Module view of a client/server system, label=moduleview, language=modulelang, belowcaptionskip=0pt]
+resource type CSIface
+	def getVal(key: String): String
+module def Client(cPlumbing: CSIface): ClientIface
+	def startClient(): Unit
+		...
+module def Server(sPlumb: SPlumbing): ServerIface
+	module def sendInfo(): CSIface
+		def getVal(key: String): String
+			...
+	def startServer(): Unit
+		sPlumb.setFn(sendInfo().getVal)
+		...
 \end{lstlisting}
 
-\lstlistingname~\ref{cncview}
+\noindent
+\textit{\textbf{Component-and-connector view.}} The component-and-connector (C\&C) view expresses runtime behavior.
+\lstlistingname{} \ref{cncview} shows the C\&C view of our example client-server system.
+It consists of two \textit{components} (i.e.
+processes): a \texttt{client} component of component type \texttt{Client} and a \texttt{server} component of component type \texttt{Client}.
+
+Components have \textit{ports} which are interfaces through which a component interacts with the components it is connected to.
+A \texttt{provides} port consists of methods that are implemented by the component, while a \texttt{requires} port consists of methods that must be implemented by a component connected to this port.
+
+For components to interact with each other, they must be connected together with a \textit{connector}.
+In \lstlistingname{} \ref{cncview}, the \texttt{client} and \texttt{server} components interact via the \texttt{jsonCtr} connector.
+The \texttt{jsonCtr} connector enables the \texttt{client} and \texttt{server} components to communicate by passing JSON data between each other.
+%The \texttt{Client} and \texttt{Server} component types correspond to the \texttt{Client} and \texttt{Server} modules in the module view respectively.
+%It is described in terms of components and connectors.
+A component is one of the principal processing units of the executing system.
+Components might be services, processes, threads, filters, repositories, peers, or clients and servers, to name a few.
+A connector is the interaction mechanism among components.
+Connectors include pipes, queues, request/reply protocols, direct invocation, event-driven invocation, etc.
+Components and connectors can be decomposed into other components and connectors.
+The decomposition of a component may include connectors and vice versa.
+
+\begin{lstlisting}[style=cncstyle, caption=C\&C view of the client/server system, label=cncview, language=cnclang, belowcaptionskip=0pt]
+component Client
+	port getInfo: requires CSIface
+component Server
+	port sendInfo: provides CSIface
+connector JSONCtr
+	val host: IPAddress
+	val prt: Int
+architecture ClientServer
+	components
+		Client client
+		Server server
+	connectors
+		JSONCtr jsonCtr
+	connections
+		connect client.getInfo and server.sendInfo
+			with jsonCtr
+\end{lstlisting}
+%
+%	entryPoints
+%		client: startClient
+%		server: startServer
+
+\noindent
+\textit{\textbf{Allocation view.}} Allocation view describes the mapping of software units to elements of an environment in which the software executes.
+In particular, software elements from the C\&C view are allocated to the hardware of the computing platform on which the software executes.
+For example, \lstlistingname{} \ref{allocationview} shows the allocation view for our client-server system.
+It specifies the IP address and port of the \texttt{server} component connected by the \texttt{jsonCtr} connector.
+%The environment might be the hardware, the file systems supporting development or deployment, or the development organization(s).
+
+\begin{lstlisting}[style=allocationstyle, caption=Allocation view of the client/server system, label=allocationview, language=allocationlang, belowcaptionskip=0pt]
+deployment CSDeployment extends ClientServer
+	jsonCtr.host = 192.168.1.1
+	jsonCtr.prt = 9090
+\end{lstlisting}
+
+\begin{lstlisting}[style=modulestyle, caption=Plumbing code generated for the client, label=clientplumbing, language=modulelang, belowcaptionskip=-5pt]
+module def cPlumbing(tcpClient: TCPClient): CSIface
+	def getVal(key: String): String
+		tcpClient.connect(IPAddress("192.168.1.1"),9090)
+		...
+
+val tcpClient = TCPClient()
+val plumbing = cPlumbing(tcpClient)
+val client = Client(plumbing)
+c.startClient()
+\end{lstlisting}
 
@@
 \\
-\textbf{Architectural Control in \langname.}
+\textbf{Architectural Control in \langname.} Communication integrity is guaranteed in \langname{} by means of the non-transitive authority property of Wyvern's capability-based module system \cite{Melicher2017}.
+For example, \lstlistingname{} \ref{clientplumbing} shows the plumbing code generated for the \texttt{client} component from the architecture description to facilitate its communication with the \texttt{server} component using the \texttt{jsonCtr} connector.
+Note in lines 6 to 8 that the \texttt{Client} module does not have a direct reference to the \texttt{TCPClient} module.
+Since authority is non-transitive in Wyvern, therefore the \texttt{Client} module would not be able to call the \texttt{connect} method of the \texttt{TCPClient} module.
+Thus, it would not be able to make connections to arbitrary hosts over the network.
 
@@
 
+\end{sloppypar}
 \end{document}
